---
title: "lab6"
author: "Benny Chen"
date: "June 15, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Population Variance

Write a function `MyVar` that calculates the population variance of a vector.  If you need a refresher of what that means, [this section of wikipedia should help](https://en.wikipedia.org/wiki/Variance#Population_variance_and_sample_variance).
```{r}
MyVar <- function(x) {
  (1/length(x))*(sum(x^2))-(mean(x)^2)
}
```
## Finding Roots
Write a function `zeroes` that finds the roots (zeroes) of a degree two polynomial.  The function should take the coefficients of the polynomial $a^2x + bx + c$ as its arguments and returns a vector of roots.  If there are no real roots, the function should stop and produce an error message: `"This polynomial has no real roots."`
```{r}
zeroes <- function(a,b,c){
  x <- ((b^2)-4*a*c)
  y <- 2*a
  if(x>=0) {
    roots <- list(z=(0-b+sqrt(x))/y,t=(0-b-sqrt(x)/y))
    return(roots)
  } else {
    stop("This polynomial has no real roots.")
  }
}
```


Test your function:
```{r, eval = F}
zeroes(1, 0, 0)
zeroes(1, 0, 1)
zeroes(1, 1, 1)
```

## Temperature Conversion

Write a function `ConvertTemperature` that takes a numeric vector of temperatures in Fahrenheit and converts them into Celsius, Kelvin, Rankine, Delisle, Newton, Reamur, or Romer, depending on what the user specifies in an argument called `to`.  If they specify some other temperature scale, return the message "The [their input] temperature scale is not supported".  If you don't know the conversions, (see this table)[https://en.wikipedia.org/wiki/Conversion_of_units_of_temperature#Fahrenheit]
```{r}
ConvertTemperature <- function(x,to) {
  if(to=="Celsius"){
    return((x-32) * 5/9)
  } else if(to=="Kelvin") {
    return((x+459.67)*5/9)
  } else if(to=="Rankine") {
    return(x+459.67)
  } else if(to=="Delisle"){
    return((212-x)*5/6)
  } else if(to=="Newton"){
    return((x-32)*11/36)
  } else if(to=="Reamur"){
    return((x-32)*4/9)
  } else if(to=="Romer") {
    return((x-32)*(7/24)+7.5)
  } else {
    return("The 'to' is not supported")
  }
}
```

Test your function
```{r, eval = F}
ConvertTemperature(32, "Celsius") == 0
ConvertTemperature(212, "Kelvin") == 373.15
ConvertTemperature(10, "Rankine") == 501.67
```


## Rolling Dice

For this problem, you'll need the `sample` and `pmax` function.  `sample` generates a random sample of a specified size either with or without replacement.  You can specify probability weights for each element of your sample space using the `prob` argument.  By default, each element will have equal probability.
```
sample(x = vector_to_be_sampled, size, replace = FALSE, prob = NULL)
```
1. What does `pmax` do? How is it different from `max`? Hint: test both on the two vectors `c(1, 5, 3)` and `c(2, 4, 2)`.
```{r}
x <- c(1,5,3)
y <- c(2,4,2)
pmax(x,y)
max(x,y)
```
pmax gives me the largest value in the matching index of the two vectors, while max gives me the maximum value of the two vectors. 

2. When you "roll dice with advantage", you roll a pair of dice and take the higher value as your roll.  Write a function `AdvRoll` the simulates rolling with advantage `n` times. The function should take on 2 arguments `sides` and `n` and output a length `n` vector of rolls.
```{r}
AdvRoll <- function(sides,n) {
  rolls1 <- sample(1:sides,n,replace=T)
  rolls2 <- sample(1:sides,n,replace=T)
  maxroll <- pmax(rolls1,rolls2)
}
```
3. Write your own summary function called `MySummary` that, given a numeric vector `x`, returns the following summary statistics: mean, median, mode, sum, and sum of squares.
```{r}
MySummary <- function(x){
  counts <- table(x)
  results <- list(mean(x),median(x),which.max(counts),sum(x),sum(x^2))
  return(results)
}
```

4. Using your two functions, simulate "rolling dice with advantage" 1000 times and find the summary statistics.
```{r}
MySummary(AdvRoll(6,1000))
```
