---
title: "hw8"
author: "Benny Chen"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
library(dplyr)
library(ggplot2)
library(RSQLite)
library(purrr)
```

### purrr

In this exercise, you'll be using functional programming ideas to simulate the central limit theorem on coin flips.  Using neither loops nor the apply functions, write a simulation pipeline that:

* Generates 1000 samples of each 1, 2, ..., 99, 100 fair coin flips.  So for example, you would simulate flipping 1 coins 1000 times, 2 coins 1000 times, etc.
* For each of the 1, 2, ..., 100 flips, produces a histogram of the proportion of heads.  To be explicit: you will create a histogram for the 1000 proportions calculated from the 1 coin flips.  Then you'll do the same for 2 coin flips, 3, etc.

In your plots
* The x-axis should be limited to 0-1
* The y-axis should be limited to 0-15


```{r, eval = FALSE}
s <- 1:100 %>% 
  map(function(x) rerun(x, sample(c(0,1), 1000, replace = T)))
  

```

Now that you have all the static images, you could "animate" the progression by turning the sequence of images into a gif.  This can be achieved with the `animation` package in R or the standalone `ImageMagick` utility.  This is just an FYI, we will not be looking for a GIF.  Also, Please do NOT upload the images to GitHub nor bCourses.  We'll just be checking your code.

## SQL

These exercises are meant to help you wrap your head around SQL.  Answer the questions below using SQL queries.  You can check your answer using `dplyr` methods, but your grade will be based on the SQL commands.  The `nycflights13` data set has been put into a SQLlite database for these problems.  For documentation about the variable names, see

```{r, eval = FALSE}
help(package = "nycflights13")
```

```{r}
flights <- src_sqlite("nycflights13.mysqlite3")
```


1. Find the full name of each airline that flew to Dallas Fort-Worth (DFW).
```{r}
flights %>% tbl(sql("
       SELECT 
         carrier,
         dest
       FROM
         nyflights
       WHERE
         dest  = 'DFW' 
        "))
```

2. Make a table containing the tail number, year of manufacture, model, number of engines, and number of seats of the planes flown by United Airlines (UA).  Sort the results by year manufactured.

```{r}
flights %>% tbl(sql("
      SELECT 
         nyplanes.tailnum,
         nyplanes.year,
         nyplanes.model,
         nyplanes.engines,
         nyplanes.seats
         tailnum
      FROM 
         nyflights INNER JOIN nyplanes
         ON nyplanes.tailnum = nyflights.tailnum
      WHERE
         carrier = 'UA'
      "))

```

3. Make a table with the following information: full airport name in a column called `Airport` and number of flights from New York City to those airports in 2013 in a column called `NumberOfFlights`.  Sort the results in descending order by flight counts.
```{r}
flights %>% tbl(sql("
           SELECT
              name AS Airport,
              COUNT(faa) AS NumberofFlights
           FROM
              nyairports INNER JOIN nyflights
              ON nyairports.faa = nyflights.dest
           GROUP BY
              dest
           ORDER BY  
              NumberofFlights desc
           "))
```

4. Find the wind speed during the hour of the sceduled departure time of every flight that had a departure delay of more than 30 minutes.  For example, if a flight was scheduled to leave at 5:59am, you would check the wind speed for 5:00am.  In practice, you would of course be more careful than this.
```{r}
flights %>% tbl(sql("
              SELECT 
                 wind_speed,
                 nyweather.hour,
                 nyflights.time_hour
              FROM
                 nyflights INNER JOIN nyweather
                 ON (nyflights.time_hour = nyweather.time_hour)
              WHERE
                 minute = 0
                 AND dep_delay >= 30
                 ")) %>%
                collect(n = Inf)
```