---
title: "Lab 7"
author: "Benny Chen"
date: "June 16, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(stringr)
knitr::opts_chunk$set(echo = TRUE)
```

## Spooky Scary
Write a function `Spooky` that uses a loop and takes `n` as its argument and prints out `"mspooky(m+2)me"` for `m = 1, ..., n`.  For example
```
> Spooky(3)
[1] "1spooky3me"
[1] "2spooky4me"
[1] "3spooky5me"
```
The function should otherwise not return anything.  Hint: A for-loop would be most appropriate here--why?
```{r}
# dis b yo kode
Spooky <- function(n){
  for(n in 1:3) {
    print(str_c(n,"spooky",(n+2),"me"))
  }
}
```
Test your code:
```{r, eval = T}
Spooky(3)
```

## Tails all the way down
Write a function `FlipTilHeads` that simulates flipping a potentially biased coin until a head appears.  The function return the number of the flip that resulted in a head. This number is called a stopping time and follows a geometric distribution. The function should have an argument `prob`, the probability of getting heads, that takes on a default value of 0.5 (a fair coin). Remember that you can use the `sample` function to help you simulate random draws.  Alternatively, if you know what the binomial distribution is, you may want to look into `rbinom`.  Hint: A while loop is probably more appropriate in this problem--why?

```{r}
# your code
FlipTilHeads <- function(n,probability=0.5){
  x <- sample(0:1,n,replace=T,prob=c(1-probability,probability))
  i <- 1
  counter <- 1
  while(x[i]!=1){
    i <- i+1
    counter <- counter +1
    }
  return(counter)
}
```

## Continued Fractions

A simple continued fraction is one of the form \[a_0 + \dfrac{1}{a_1 + \dfrac{1}{a_2 + \dfrac{1}{a_3 + ...}}}\]
The common shorthand for such a number is $\left[a_0; a_1, a_2, a_3, ...\right]$.  For example, the continued fraction form of $3.245 = 3 \frac{49}{200}$ is $\left[3; 4, 12, 4\right]$ since \[3.245 = 3 + \dfrac{1}{4 + \dfrac{1}{12 + \dfrac{1}{4}}}\]  Every number can be represented as a continued fraction.  Interestingly, unlike in decimal notation, every rational number has a finite continued fraction form (i.e. the sequence terminates), and every irrational number is an infinite continued fraction.  Using a loop, write a function `CFracToDec` that takes a vector representing a continued fraction and converts it into its decimal form.  For example:
```{r, eval = F}
x <- c(3, 4, 12, 4)
CFracToDec(x)
```
should return 3.245.  Hint: The index set of the for-loop might not be of the form `1, 2, ..., n`.

```{r}
# your code
CFracToDec <- function(x){
    x <-rev(x)
    a=0
    for(i in 1:length(x)){
       a<-(1/a)+x[i]
    }
    return(a)
}
```
Test your function 
```{r, eval = T}
CFracToDec(c(3, 4, 12, 4)) # 3.245
CFracToDec(c(3,7,15,1,292,1,1,1,2,1,3,1)) # 3.141593
CFracToDec(c(2,1,2,1,1,4,1,1,6,1,1,8)) # 2.718282
```

## Hailstone Sequences 
Given a positive integer, consider the following rules:

* If the number is even, divide it by two
* If the number is odd, triple it and add one

The Collatz Conjecture posits that if you repeatedly apply these rules, then eventually you will always end up at 1.  The path that the number takes from start to end is called a _hailstone sequence_ because of the multiple ascents and descents the number takes.  Let's assume the conjecture is true.  Write a function called `Hailstone` that, when given a positive integer `n`, applies the above procedure until the sequence hits 1 or your computer dies.  The function should return two __named__ objects:

* sequence - a vector containing the start value, the intermediate values, and end value
* stop_time - an integer denoting how many steps it took for the sequence to terminate

```{r}
Hailstone <- function(n){
  sequences <- c(n)
  if(n%%2==0){
    counter <- 0
    while(n%%2==0){
      n <- n/2
      counter <- counter +1
      sequences[counter] <- n
     while(n%%2!=0){ 
        n <- 3*n+1
        counter <- counter +1
        sequences[counter] <- n
     } 
    }
    
  } else {
      counter <- 0
      while(n%%2!=0 & n !=1){
        n <- 3*n+1
        counter <- counter +1
        sequences[counter+1] <- n
      while(n%%2==0 & n!=1){
        n <- n/2
        counter <- counter +1
        sequences[counter+1] <- n
      }
      }
  }
   stop_time <- counter
   print(c(sequences,stop_time))
}
  
```
Test your function:
```{r, eval = T}
Hailstone(1) # sequence = 1; stop_time = 0
Hailstone(5) # sequence = (5, 16, 8, 4, 2, 1); stop_time = 5
Hailstone(27) # sequence = too long for this comment; stop_time = 111
```

