---
title: "lab1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Answer the following questions programmatically.  You should submit a `.R` file to bCourses and upload a copy of your work to your GitHub account.

# Data
Here is some data about the Raiders during a particular superbowl season

```{r raiders}
scored <- c(14, 14, 9, 14, 28, 13, 13, 24, 17, 6, 24, 0, 24, 13, 26, 14)
against <- c(19, 30, 16, 38, 31, 24, 23, 30, 41, 13, 20, 52, 13, 31, 24, 47)
```

# Part 1
These questions refer to the vector `scored`

1. How many points did the Raiders score in game 7?
```{r}
scored[7]
```

2. What was the score of the first 5 games?
```{r}
scored[c(1:5)]
```
3. What were the scores of the even games? Try to do this problem without typing in c(2,4,...)
```{r}
scored[c(seq(2,length(scored),2))]
```

4. What was the score of the last game? Try to do this problem without typing in the number of the last game.
```{r}
tail(scored,1)
```

5. Select the scores higher than 14.
```{r}
scored[scored>14]
```

6. Select the scores equal to 14.
```{r}
scored[scored==14]
```

7. Select the scores equal to 13 or 14.
```{r}
scored[scored==13 | scored ==14]
```
8. Select the scores between between 7 and 21 points.
```{r}
scored[scored>7 & scored < 21]
```

9. Sort the scores in decreasing order.
```{r}
sort(scored,decreasing=T)
```
10. What was the highest score achieved?
```{r}
head(sort(scored,decreasing=T),1)
```

11. What was the lowest score achieved?
```{r}
head(sort(scored),1)
```

12. What was the average score?
```{r}
mean(scored)
```

13. Use the `summary()` function to give some summary statistics.
```{r}
summary(scored)
```

14. In how many games did the Raiders score over 20 points?
```{r}
length(scored[scored>20])
```


# Part 2
These questions refer to both vectors.

1. What was the sum of the scores in game 7?
```{r}
scored[7]+against[7]
```

2. What was the sum of the scores in each of the last 5 games?
```{r}
tail(scored,5) +tail(against,5)
```

3. What was the difference in scores in each of the odd games?
```{r}
scored[c(seq(1,length(scored),2))] - against[c(seq(1,length(scored),2))]
```

4. Which games did the Raiders win?
```{r}
which(scored > against)
```

5. Were there any ties?
```{r}
length(scored[scored == against])
```

